A_pilot_1

### 2018-08-30 experiments/A_pilot_1/writeup/A_pilot_1.Rmd
applied custom .css to A

---
title: "A_pilot_1"
author: "Matt Green"
output:
  html_document:
    toc: yes
---

@@

```{r plot rt per trial by subject}
dat %>% 
  gather(key=rt_metric, value=rt_value, rt_ms, rt_log, rt_reciprocal) %>%
  filter(rt_metric=="rt_log") %>%
  ggplot(aes(x=trial, y=rt_value, col=vag)) +
  geom_point() +
  geom_smooth(se=F) +
  facet_wrap(~subject) +
  theme(aspect.ratio = 1, panel.background = element_rect(fill="white", colour="black", linetype = "solid"))
```

@@

```{r lmer on logrt, warning=FALSE, cache=TRUE}
lmer2.log <- lmer(data=dat, rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))
dwplot(lmer2.log %>% tidy() %>% filter(group=="fixed")) + ggtitle("rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)")

@@

# lmer3 is closer to the original anova than lmer2
lmer3 <- tidy(lmer(data=dat, rt_reciprocal~vag*subit+quan+gap + (vag+subit|subject) + (vag|item)))
dwplot(lmer3 %>% filter(group=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2)) + xlab("Coefficient")
```

>>>>

---
title: "A_pilot_1"
author: "Matt Green"
output:
  html_document:
    toc: yes
    theme: default
    css: styles.css
---

@@

```{r plot rt per trial by subject}
dat %>% 
  gather(key=rt_metric, value=rt_value, rt_ms, rt_log, rt_reciprocal) %>%
  filter(rt_metric=="rt_log") %>%
  ggplot(aes(x=trial, y=rt_value, col=vag)) +
  geom_point() +
  geom_smooth(se=F) +
  facet_wrap(~subject, ncol = 7) +
  theme(aspect.ratio = 1, panel.background = element_rect(fill="white", colour="black", linetype = "solid"))
```

@@

```{r lmer on logrt, warning=FALSE, cache=TRUE, fig.width=6, fig.height=2}
lmer2.log <- lmer(data=dat, rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))

dwplot(lmer2.log %>% tidy() %>% filter(group=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) +
  xlab("Coefficient") +
  ggtitle("rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)") + 
  theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8))

@@

# lmer3 is closer to the original anova than lmer2
lmer3 <- lmer(data=dat, rt_reciprocal~vag*subit+quan+gap + (vag+subit|subject) + (vag|item))

dwplot(lmer3 %>% tidy() %>% filter(group=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 1)) +
  xlab("Coefficient") + 
  ggtitle("rt_reciprocal ~ vag * subit + quan + gap + (vag+subit|subject) + (vag|item)") + 
  theme(plot.title = element_text(size = 8), axis.title.x = element_text(size=8), axis.text.x = element_text(size=8))
```
